---
title: "Chile Text Mining"
author: "León Hernández Robles"
date: "8/27/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rtweet)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```




## Slide with Intro
Chile se encuentra a unos días de llevar a cabo un plebiscito para aprovar, o 
rechazar, la nueva constitución propuesta por el gobierno de Gabriel Boric.

En este ejercicio, se presentan tendencias en los tweets relacionados a este
evento.

## Slide with library loading
<code>library(tm)\
library(tidytext)\
library(tidyr)\
library(dplyr)\
library(ggplot2)\
library(stringr)\
library(tidytext)\
library(wordcloud)\
library(textdata)\
library(rtweet)\
library(tidyverse)
</code>



## Data Extraction
```{r, echo=TRUE}
chile = search_tweets(q="boric OR chile OR constitucion OR apruebo OR rechazo",
                      n = 1000,
                      )
```
```{r, echo=TRUE}
dim(chile)
```


## Limpieza de datos


